### 2023-09-29 chapters/main-contributions.tex
Updates to citation commands and footnotes

\contribitem{chp:paper-benchmarking}
This paper proposes a new hierarchical variational autoencoder for speech inspired by the Clockwork VAE \cite{saxena_clockwork_2021}. 
The model is benchmarked against other variational autoencoders and autoregressive models for speech. We show that using a hierarchy of latent variables improves the likelihood of the model and that the learned latent space captures information relevant for speech recognition such as phonetic content.

\contribitem{part:self-supervised-speech-representation-learning}
This part of the thesis is concerned with self-supervised speech representation learning and consists of a single paper that provides a substantial review of the field \cite{mohamed_selfsupervised_2022}. 
Self-supervised learning is a promising approach to speech representation learning that has shown a fast, wide and successful adoption across speech modelling over the course of the last few years. 
As measured by performance on common downstream tasks such as speech recognition and spoken language understanding, self-supervised representations generally outperform representations learned via probabilistic generative models such as those investigated in \cref{part:unsupervised-uncertainty-estimation}. 
In this review paper, we do not consider uncertainty estimation, but in future work, consideration should be given to the use of self-supervised learning as an alternative paradigm to generative models for learning representations for unsupervised uncertainty estimation. We shall return to this in the discussion of \cref{chp:paper-review} in \cref{sec:discussion-paper-review}.

@@

An early version of this review paper \cite{borgholt_brief_2022} included a review of generative latent variable models for speech representation learning and a comparison between the two modelling paradigms. 
Due to the superior performance of self-supervised methods and a desire to focus on self-supervised methods, the paper in \cref{chp:paper-review} does not focus on generative latent variable models. 
The early version is included in \cref{app:paper-brief} for reference.

>>>>

\contribitem{chp:paper-benchmarking}
This paper proposes a new hierarchical variational autoencoder for speech inspired by the Clockwork VAE \parencite{saxena_clockwork_2021}. 
The model is benchmarked against other variational autoencoders and autoregressive models for speech. We show that using a hierarchy of latent variables improves the likelihood of the model and that the learned latent space captures information relevant for speech recognition such as phonetic content.

\contribitem{part:self-supervised-speech-representation-learning}
This part of the thesis is concerned with self-supervised speech representation learning and consists of a single paper that provides a substantial review of the field \parencite{mohamed_selfsupervised_2022}. 
Self-supervised learning is a promising approach to speech representation learning that has shown a fast, wide and successful adoption across speech modelling over the course of the last few years. 
As measured by performance on common downstream tasks such as speech recognition and spoken language understanding, self-supervised representations generally outperform representations learned via probabilistic generative models such as those investigated in \cref{part:unsupervised-uncertainty-estimation}. 
In this review paper, we do not consider uncertainty estimation, but in future work, consideration should be given to the use of self-supervised learning as an alternative paradigm to generative models for learning representations for unsupervised uncertainty estimation. We shall return to this in the discussion of \cref{chp:paper-review} in \cref{sec:discussion-paper-review}.

@@

An early version of this review paper \parencite{borgholt_brief_2022} included a review of generative latent variable models for speech representation learning and a comparison between the two modelling paradigms. 
Due to the superior performance of self-supervised methods and a desire to focus on self-supervised methods, the paper in \cref{chp:paper-review} does not focus on generative latent variable models. 
The early version is included in \cref{app:paper-brief} for reference.
